\documentclass[line,margin]{res}
\begin{document}
\name{Stewart S. Grant}
\address{https://www.stewartgrant.ca}
\address{ssgrant@eng.ucsd.edu}
%%\address{(619) 550-7315}
%%\address{2601, 3869 Miramar Street}
\begin{resume}

    \section{PUBLICATIONS (Papers)}

{\sl 
    SmartNIC Performance Isolation with FairNIC \\
    Stewart Grant, Anil Yelam, Maxwell Bland, Alex Snoeren\\
    Sigcomm 2020 \\
    }

{\sl 
    Inferring and Asserting Distributed System Invariants. \\
    Stewart Grant, Hendrick Cech, Ivan Beschastnikh. \\
    International Conference on Software Engineering ICSE 2018 \\
    }

{\sl 
    Dancing in the Dark: Private Multi-Party Machine Learning in an Untrusted Setting \\
    Clement Fung, Jamie Koerner, Stewart Grant, Ivan Beschastnikh \\
    Archive 2019
    }

\section{PUBLICATIONS (Posters)}

{\sl Stewart Grant, Ivan Beschastnikh. 
    Distributed Test Case Generation using Model Inference with Dara
    \it{Proceedings of the 15th
    USENIX Symposium on Networked Systems Design and Implementation, NSDI 2018},
    Renton, Washington, USA. (Poster)}

{\sl Stewart Grant, Sam Creed, Ivan Beschastnikh. Inferring data
    invariants in distributed systems. In \it{Proceedings of the 25th
    ACM Symposium on Operating Systems Principles, SOSP 2015},
    Monterey, California, USA. (Poster)}


\section{RESEARCH PROJECTS}

{\sl Warm} [In devlopment] \hfill 2021\\
    Resolving write contention for disaggregated memory
\begin{itemize} \itemsep -2pt
        \item Warm reorganizes RDMA calls in flight to accelerate access to disaggregated data structures.
        \item https://github.com/wantonsolutions/warm
\end{itemize}

{\sl Doppleganger} [In devlopment] \hfill 2021\\
    Sub RTT replica selection in data centers
\begin{itemize} \itemsep -2pt
        \item microsecond level load balancing for bursty data center networks.
        \item https://github.com/ucsdsysnet/replica-selection
\end{itemize}

{\sl FairNIC } \hfill 2020\\
    Fair sharing on SmartNIC's
\begin{itemize} \itemsep -2pt
        \item FairNIC isolates SmartNIC resources so multiple applications can colocate.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://github.com/wantonsolutions/NetCrash
\end{itemize}

{\sl Dara \hfill 2017\\
    Distributed dynamic verification
\begin{itemize} \itemsep -2pt
        \item Dara models distributed systems from execution logs. Models are checked against specifications.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://github.com/wantonsolutions/dara
\end{itemize}

{\sl TorMentor} \hfill 2017\\
    Anonymous multi party machine learning
\begin{itemize} \itemsep -2pt
        \item A collaborative machine learning framework that operates through Tor.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://github.com/DistributedML/TorML
\end{itemize}


{\sl Dinv} \hfill 2015-2018\\
    Distributed System Invariant Detector
\begin{itemize} \itemsep -2pt
        \item Developed novel distributed state merging algorithms, and automatic instrumentation techniques.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://bitbucket.org/bestchai/dinv
\end{itemize}


\section{EDUCATION}
{\sl PhD,} Computer Science \\
University of California San Diego \\
Expected 2024 \\

{\sl MSc,} Computer Science \hfill 2018 \\
University of British Colombia, Vancouver, BC \\

{\sl Bachelors of Science,} Computer Science	\hfill 2016\\
University of British Colombia, Vancouver, BC \\

{\sl Associate of Science,} Computer Science \hfill 2011-2013\\
Langara College, Vancouver, BC\\


\section{EMPLOYMENT} 

{\sl Teaching Assistant UCSD} \hfill 2021\\
	University of California San Diego
\begin{itemize} \itemsep -2pt
        \item One semester TA in distributed systems 223B \hfill 2021
	\end{itemize}

{\sl Research Intern} \hfill 2017\\
    INRIA Rennes 1, ASAP (As scalable as possible)
\begin{itemize} \itemsep -2pt
        \item Built a framework for model checking distributed, from runtime logs
    \end{itemize}

{\sl Research Assistant} \hfill 2017\\
    University of British Columbia, Under Ivan Beschastnikh
\begin{itemize} \itemsep -2pt
        \item Oversaw various research projects
    \end{itemize}

{\sl Undergraduate Research Assistant} \hfill 2015-2016\\
	University of British Columbia, Department of Computer Science
\begin{itemize} \itemsep -2pt
        \item Designed and developed Dinv, a tool for checking data invariants in distributed system.
    \end{itemize}


{\sl Teaching Assistant UBC} \hfill 2015-2016\\
	University of British Columbia, Department of Computer Science
\begin{itemize} \itemsep -2pt
        \item One semester TA in distributed systems 416 \hfill 2017
		\item Three semester TA in software engineering 310 \hfill 2015-2016\\
	\end{itemize}
{\sl Lab Assignment Author} \hfill 2013\\
	Langara College Computer Science Department
	\begin{itemize} \itemsep -2pt
			\item Developed lab assignments for Object Oriented Programming, and introduction to assembly, CPSC 1181, and 2180 respectively.
	\end{itemize}
    

\section{AWARDS}
{\sl NSERC USRA Award} \hfill 2016\\
{\sl Rick Sample Summer Internship} \hfill 2015\\
{\sl Science Undergraduate Research Experience Award} \hfill 2015\\


\section{VOLUNTEER}

{\sl Effective Writing Group Organizer} {\hfill 2019 - 2020}
    \begin{itemize}
        \item Group and lesson organizer, discussion lead
    \end{itemize}

{\sl Faculty Candidate Student Panel Organizer} {\hfill 2019}
    \begin{itemize}
        \item Ran weekly intervew group discussions with faculty
            candidates, and interested PhD students
     \end{itemize}

{\sl Conference Volunteering} \hfill 2017
    \begin{itemize}
        \item Student Voulenteer SPLASH 2017
    \end{itemize}

{\sl Reviewing} \hfill 2017
    \begin{itemize}
        \item ACM CHI 2018
        \item Journal of Systems and Software
    \end{itemize}

{\sl Computer Science Student Society Officer} \hfill 2015
    \begin{itemize}
        \item Assisted with fund raisers, and event organization
        \item Volunteered with treasury for money counts
    \end{itemize}

{\sl OWL ( Orphaned Wildlife Foundation )} {\hfill 2007 - 2008}
    \begin{itemize}
         \item Assisted in the rehabilitation, and ongoing care of injured birds of prey
    \end{itemize}
}

\section{COMPUTER \\ SKILLS} 
	{\sl Programming Languages:} C, Go, C++, Bash, Python\\
	{\sl Operating System:} Linux, Windows\\
	{\sl Text Manipulation:} Vim, Git, \LaTeX \\

\section{INTERESTS}
	{\sl Computing:}  Distributed Systems, Networking, Resource Disaggregation.\\
	{\sl Extra Curricular:} Rock Climbing, Experimental Music, Hiking, Juggling, Twisty Puzzles.\\

\end{resume}
\end{document}

