\documentclass[line,margin]{res}
\begin{document}
\name{Stewart S. Grant}
\address{3549 Puget Drive, Vancouver, BC }
\address{(604) 970-2469}
\address{sgrant09@cs.ubc.ca}
\address{https://wantonsolutions.github.io/}
\begin{resume}

\section{RESEARCH}

{\sl Dara [In development]} \hfill 2017\\
    Distributed dynamic verification
\begin{itemize} \itemsep -2pt
        \item Dara models distributed systems from execution logs. Models are checked against specifications.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://github.com/wantonsolutions/dara
\end{itemize}

{\sl Dviz [In development]} \hfill 2016\\
    Distributed State Visualizer
\begin{itemize} \itemsep -2pt
        \item Pangaea plots distributed snapshots by grouping snapshots with similar states.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://www.github.com/zipengliu/Pangaea
\end{itemize}

{\sl Dinv} \hfill 2015-2017\\
    Distributed System Invariant Detector
\begin{itemize} \itemsep -2pt
        \item Developed novel distributed distributed state merging algorithms, and automatic instrumentation techniques.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://bitbucket.org/bestchai/dinv
\end{itemize}
{\sl \textit{All research mentored by Dr.Ivan Beschastnikh}}\\

\section{PUBLICATIONS}

{\sl 
    Inferring and Asserting Distributed System Invariants. \\
    Stewart Grant, Hendrick Cech, Ivan Beschastnikh. 
    \it{Currently under submissions}}

{\sl Stewart Grant, Sam Creed, Ivan Beschastnikh. Inferring data invariants in distributed systems. In \it{Proceedings of the 25th ACM Symposium on Operating Systems Principles, SOSP 2015}, Monterey, California, USA. (Poster)}

\section{EDUCATION}
{\sl MSc,} Computer Science\\
University of British Colombia, Vancouver, BC \\
Expected 2018

{\sl Bachelors of Science,} Computer Science	\hfill 2016\\
University of British Colombia, Vancouver, BC \\

\section{EMPLOYMENT} 
{\sl Research Intern} \hfill 2017\\
    INRIA Rennes 1, ASAP (As scalable as possible)
\begin{itemize} \itemsep -2pt
        \item Built a framework for model checking distributed, from runtime logs
    \end{itemize}
{\sl Research Assistant} \hfill 2017\\
    University of British Columbia, Under Ivan Beschastnikh
\begin{itemize} \itemsep -2pt
        \item Oversaw various research projects
    \end{itemize}
{\sl Teaching Assistant} \hfill 2015-2016\\
	University of British Columbia, Department of Computer Science
\begin{itemize} \itemsep -2pt
        \item One semester TA in distributed systems 416 \hfill 2017
		\item Three semester TA in software engineering 310 \hfill 2015-2016\\
	\end{itemize}

\section{AWARDS}
{\sl NSERC USRA Award} \hfill 2016\\
{\sl Rick Sample Summer Internship} \hfill 2015\\
{\sl Science Undergraduate Research Experience Award} \hfill 2015\\


\section{VOLUNTEER}

{\sl Reviewer} \hfill 2017
    \begin{itemize}
        \item Journal of Systems and Software
    \end{itemize}

{\sl Computer Science Student Society Officer} \hfill 2015
    \begin{itemize}
        \item Assisted with fund raisers, and event organization
        \item Volunteered with treasury for money counts
    \end{itemize}

\section{COMPUTER \\ SKILLS} 
	{\sl Programming Languages:} Go, C, Bash, JavaScript, Java\\
	{\sl Operating System:} Linux, Windows\\
	{\sl Text Manipulation:} Vim, Git, \LaTeX \\

\section{INTERESTS}
	{\sl Computing:}  Distributed Systems, Operating Systems, Algorithm Design and implementation, and System Analysis.\\
	{\sl Extra Curricular:} Rock Climbing, Experimental Music, Hiking, Juggling.\\

\end{resume}
\end{document}

