\documentclass[line,margin]{res}
\begin{document}
\name{Stewart S. Grant}
\address{3549 Puget Drive, Vancouver, BC }
\address{(604) 970-2469}
\address{v9c9@ugrad.cs.ubc.ca}
\begin{resume}
\section{RESEARCH}
{\sl DInv} \hfill 2015\\
    Distributed System Invariant Detector
\begin{itemize} \itemsep -2pt
        \item DInv detects data invariants in distributed systems by capturing dataflow between hosts, and relating it temporally.
        \item Expanded the system to capture temporal interactions across an arbitrary number of hosts, and to analyse Go source code across multiple repositories
        \item Developed and implemented algorithms for ordering, and associating dataflow across multiple hosts.
        \item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://bitbucket.org/bestchai/dinv
\end{itemize}

{\sl Repograms} \hfill 2015\\
	Code Repository Visualization, and Comparison Tool
\begin{itemize} \itemsep -2pt
        \item Repograms visualizes development metrics in Git code repositories to assist researchers in their choice of code bases to study.
        \item Developed three analysis metrics, providing proximate development time for researches unfamiliar with the tool.
        \item Research mentored by Daniel Rozenberg M.S \& Dr.Ivan Beschastnikh, University of British Columbia
		\item http://repograms.net
\end{itemize}

\section{PUBLICATIONS}
{\sl Stewart Grant, Sam Creed, Ivan Beschastnikh. Inferring data invariants in distributed systems. In \it{Proceedings of the 25th ACM Symposium on Operating Systems Principles, SOSP 2015}, Monterey, California, USA. (Poster)}

\section{EDUCATION}
{\sl Bachelors of Science,} Computer Science	\hfill 2015\\
University of British Colombia, Vancouver, BC \\
Expected: 2015

{\sl Associate of Science,} Computer Science \hfill 2011-2013\\
Langara College, Vancouver, BC\\


\section{EMPLOYMENT} 
{\sl Undergraduate Research Assistant} \hfill 2015\\
	University of British Columbia, Department of Computer Science
\begin{itemize} \itemsep -2pt
        \item Designed and developed Dinv, a tool for detecting data invariants in distributed system.
    \end{itemize}
{\sl Teaching Assistant} \hfill 2015\\
	University of British Columbia, Department of Computer Science
\begin{itemize} \itemsep -2pt
		\item Oversaw the development of web applications, involving distributed data persistence, Social media integration, and user interface design.
	\end{itemize}
{\sl Lab Assignment Author} \hfill 2013\\
	Langara College Computer Science Department
	\begin{itemize} \itemsep -2pt
			\item Developed lab assignments for Object Oriented Programming, and introduction to assembly, CPSC 1181, and 2180 respectively.
	\end{itemize}

\section{AWARDS}
{\sl Rick Sample Summer Internship} \hfill 2015\\
{\sl Science Undergraduate Research Experience Award} \hfill 2015\\


\section{VOLUNTEER}
{\sl Computer Science Student Society Officer} \hfill 2015
    \begin{itemize}
        \item Assisted with fund raisers, and event organization
        \item Volunteered with treasury for money counts
    \end{itemize}

{\sl OWL ( Orphaned Wildlife Foundation ) {\hfill 2007 - 2008}
    \begin{itemize}
         \item Assisted in the rehabilitation, and ongoing care of injured birds of prey
    \end{itemize}
}
    

\section{COMPUTER \\ SKILLS} 
	{\sl Programming Languages:} C, Go, Java, Bash, Ruby, MASM\\
	{\sl Operating System:} Linux, Windows\\
	{\sl Text Manipulation:} Vim, Git, \LaTeX \\

\section{INTERESTS}
	{\sl Computing:} Operating Systems, Distributed Systems, Algorithm Design and implementation, and System Analysis.\\
	{\sl Extra Curricular:} Rock Climbing, Experimental Music, Hiking, Gardening.\\

\end{resume}
\end{document}

