\documentclass[line,margin]{res}
\begin{document}
\name{Stewart S. Grant}
\address{https://www.stewartgrant.ca}
\address{ssgrant@eng.ucsd.edu}
%%\address{(619) 550-7315}
%%\address{2601, 3869 Miramar Street}
\begin{resume}

    \section{PUBLICATIONS (Papers)}

{\sl 
    SwordBox: Sharing Disaggregated Memory without Skewing Performance \\
    Stewart Grant, Alex Snoeren\\
    [Currently under submission] 2022 \\
    }
{\sl 
    Daronpon: Datacenter-scale Sub-RTT Replica Selection for Low-latency Applications \\
    Shu-Ting Wang, Stewart Grant, George Porter, Alex Snoeren\\
    [Currently under submission] 2022 \\
    }
{\sl 
    In-network Contention Resolution for Disaggregated Memory \\
    Stewart Grant, Alex Snoeren\\
    WORDS 2021 \\
    }

{\sl 
    SmartNIC Performance Isolation with FairNIC \\
    Stewart Grant, Anil Yelam, Maxwell Bland, Alex Snoeren\\
    Sigcomm 2020 \\
    }

{\sl 
    Inferring and Asserting Distributed System Invariants. \\
    Stewart Grant, Hendrick Cech, Ivan Beschastnikh. \\
    International Conference on Software Engineering ICSE 2018 \\
    }

{\sl 
    Dancing in the Dark: Private Multi-Party Machine Learning in an Untrusted Setting \\
    Clement Fung, Jamie Koerner, Stewart Grant, Ivan Beschastnikh \\
    Archive 2019
    }

\section{PUBLICATIONS (Posters)}

{\sl Stewart Grant, Ivan Beschastnikh. 
    Distributed Test Case Generation using Model Inference with Dara
    \it{Proceedings of the 15th
    USENIX Symposium on Networked Systems Design and Implementation, NSDI 2018},
    Renton, Washington, USA. (Poster)}

{\sl Stewart Grant, Sam Creed, Ivan Beschastnikh. Inferring data
    invariants in distributed systems. In \it{Proceedings of the 25th
    ACM Symposium on Operating Systems Principles, SOSP 2015},
    Monterey, California, USA. (Poster)}


\section{RESEARCH PROJECTS}

{\sl Swordbox} \hfill 2021\\
    Resolving write contention for disaggregated memory
\begin{itemize} \itemsep -2pt
        \item Warm reorganizes RDMA calls in flight to accelerate access to disaggregated data structures.
        \item https://github.com/wantonsolutions/warm
\end{itemize}

{\sl Daronpon} \hfill 2021\\
    Sub RTT replica selection in data centers
\begin{itemize} \itemsep -2pt
        \item microsecond level load balancing for bursty data center networks.
        \item https://github.com/ucsdsysnet/replica-selection
\end{itemize}

{\sl FairNIC } \hfill 2020\\
    Fair sharing on SmartNIC's
\begin{itemize} \itemsep -2pt
        \item FairNIC isolates SmartNIC resources so multiple applications can colocate.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://github.com/wantonsolutions/NetCrash
\end{itemize}

{\sl Dara \hfill 2017\\
    Distributed dynamic verification
\begin{itemize} \itemsep -2pt
        \item Dara models distributed systems from execution logs. Models are checked against specifications.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://github.com/wantonsolutions/dara
\end{itemize}

{\sl TorMentor} \hfill 2017\\
    Anonymous multi party machine learning
\begin{itemize} \itemsep -2pt
        \item A collaborative machine learning framework that operates through Tor.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://github.com/DistributedML/TorML
\end{itemize}

{\sl Dviz} \hfill 2016\\
    Distributed State Visualizer
\begin{itemize} \itemsep -2pt
        \item Pangaea plots distributed snapshots by grouping snapshots with similar states.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://ww            <p> TorMentor is a collaborative machine learning framework that operates through Tor. TorMentor clients participate in a federated learning algorithm. Clients are protected from the de-anonymization of their data via differential privacy.</p>
w.github.com/zipengliu/Pangaea
\end{itemize}

{\sl Obeah} \hfill 2016\\
    SMT guided distributed fuzz tester
\begin{itemize} \itemsep -2pt
        \item Obeah fuzzes systems by modifying messages specifically to trigger unusual control flow.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://www.github.com/wantonsolutions/obeah
\end{itemize}

{\sl Dinv} \hfill 2015-2018\\
    Distributed System Invariant Detector
\begin{itemize} \itemsep -2pt
        \item Developed novel distributed state merging algorithms, and automatic instrumentation techniques.
        %\item Research Mentored by Dr.Ivan Beschastnikh, University of British Columbia
        \item https://bitbucket.org/bestchai/dinv
\end{itemize}

{\sl Dovid} \hfill 2015-2016\\
    Distributed System Documenter
\begin{itemize} \itemsep -2pt
        \item Dovid automatically generated documentation for distributed systems.
        \item Documentation includes descriptions of variables affected, and affecting network traffic, and network communication points.
        %\item Research Mentored by Dr.Ivan Beschastnikh and Dr.Reid Holmes, University of British Columbia
        \item https://bitbucket.org/wantonsolutions/Dovid
\end{itemize}

{\sl Repograms} \hfill 2015\\
	Code Repository Visualization, and Comparison Tool
\begin{itemize} \itemsep -2pt
        \item Developed three analysis metrics, providing proximate development time for researches unfamiliar with the tool.
		\item http://repograms.net
\end{itemize}


\section{EDUCATION}
{\sl PhD,} Computer Science \\
University of California San Diego \\
Expected 2024 \\

{\sl MSc,} Computer Science \hfill 2018 \\
University of British Colombia, Vancouver, BC \\

{\sl Bachelors of Science,} Computer Science	\hfill 2016\\
University of British Colombia, Vancouver, BC \\

{\sl Associate of Science,} Computer Science \hfill 2011-2013\\
Langara College, Vancouver, BC\\


\section{EMPLOYMENT} 

{\sl Teaching Assistant UCSD} \hfill 2021\\
	University of California San Diego
\begin{itemize} \itemsep -2pt
        \item One semester TA in distributed systems 223B \hfill 2021
	\end{itemize}

{\sl Research Intern} \hfill 2017\\
    INRIA Rennes 1, ASAP (As scalable as possible)
\begin{itemize} \itemsep -2pt
        \item Built a framework for model checking distributed, from runtime logs
    \end{itemize}

{\sl Research Assistant} \hfill 2017\\
    University of British Columbia, Under Ivan Beschastnikh
\begin{itemize} \itemsep -2pt
        \item Oversaw various research projects
    \end{itemize}

{\sl Undergraduate Research Assistant} \hfill 2015-2016\\
	University of British Columbia, Department of Computer Science
\begin{itemize} \itemsep -2pt
        \item Designed and developed Dinv, a tool for checking data invariants in distributed system.
    \end{itemize}


{\sl Teaching Assistant UBC} \hfill 2015-2016\\
	University of British Columbia, Department of Computer Science
\begin{itemize} \itemsep -2pt
        \item One semester TA in distributed systems 416 \hfill 2017
		\item Three semester TA in software engineering 310 \hfill 2015-2016\\
	\end{itemize}
{\sl Lab Assignment Author} \hfill 2013\\
	Langara College Computer Science Department
	\begin{itemize} \itemsep -2pt
			\item Developed lab assignments for Object Oriented Programming, and introduction to assembly, CPSC 1181, and 2180 respectively.
	\end{itemize}
    

\section{AWARDS}
{\sl Meta PhD Fellowship \hfill 2022} \\
{\sl NSERC USRA Award} \hfill 2016\\
{\sl Rick Sample Summer Internship} \hfill 2015\\
{\sl Science Undergraduate Research Experience Award} \hfill 2015\\


\section{VOLUNTEER}

{\sl Effective Writing Group Organizer} {\hfill 2019 - 2020}
    \begin{itemize}
        \item Group and lesson organizer, discussion lead
    \end{itemize}

{\sl Early Research Scholars Program} {\hfill 2019 - 2020}
    \begin{itemize}
        \item Phd advisor for 4 undergraduate students
    \end{itemize}

{\sl Faculty Candidate Student Panel Organizer} {\hfill 2019}
    \begin{itemize}
        \item Ran weekly intervew group discussions with faculty
            candidates, and interested PhD students
     \end{itemize}

{\sl Conference Volunteering} \hfill 2017
    \begin{itemize}
        \item Student Voulenteer SPLASH 2017
    \end{itemize}

{\sl Reviewing} \hfill 2017
    \begin{itemize}
        \item ACM CHI 2018
        \item Journal of Systems and Software
    \end{itemize}

{\sl Computer Science Student Society Officer} \hfill 2015
    \begin{itemize}
        \item Assisted with fund raisers, and event organization
        \item Volunteered with treasury for money counts
    \end{itemize}

{\sl OWL ( Orphaned Wildlife Foundation )} {\hfill 2007 - 2008}
    \begin{itemize}
         \item Assisted in the rehabilitation, and ongoing care of injured birds of prey
    \end{itemize}
}
    

\section{COMPUTER \\ SKILLS} 
	{\sl Programming Languages:} Go, C, Bash, JavaScript, Java\\
	{\sl Operating System:} Linux, Windows\\
	{\sl Text Manipulation:} Vim, Git, \LaTeX \\

\section{HOBBY \\ PROJECTS}
{\sl Distributed Clocks} \hfill 2015-2017\\
    Optimized inter-operable vector clock library
\begin{itemize} \itemsep -2pt
		\item Distributed clocks implements vector clocks in Go, Java, C++ and C
		\item https://github.com/DistributedClocks
\end{itemize}

{\sl Pollock} \hfill 2015\\
	Abstract Github contribution visualizer
\begin{itemize} \itemsep -2pt
		\item Pollock generates splatter painting based on the contribution history of Github repositories. The Thickness and direction of the paint splatters is derived from the individual contributors, and the frequency and volume of their commits.
		\item Written in, Java, Bash, Ruby, Processing2
		\item https://github.com/wantonsolutions/Pollock
\end{itemize}

{\sl ChocOS} \hfill 2015\\
	Operating System Kernel
\begin{itemize} \itemsep -2pt
		\item ChocOS is a minimal operating system, providing memory management, process scheduling, keyboard IO, and IPC via signalling and message passing.
		\item written in C
		\item https://github.com/wantonsolutions/ChocOS
\end{itemize}

\section{INTERESTS}
	{\sl Computing:}  Distributed Systems, Operating Systems, Algorithm Design and implementation, and System Analysis.\\
	{\sl Extra Curricular:} Rock Climbing, Experimental Music, Hiking, Juggling.\\

\end{resume}
\end{document}

